Resurgence of the Airy function \\ and other exponential integrals

### 2022-08-19 Introduction.tex

Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. Moreover, in the examples, $\hat{\varphi}_\alpha(\zeta)$ turn out be an hypergeometric function of type ${}_pF_{p-1}$ where $p$ is the number of critical points. 
We expect that hypergeometric functions play a special role in resurgence theory as they may always appear when there are only finitely many singularities. In addition,  \textbf{Aaron-> what do you expect to be true in terms of the algebraic hypergeometric?}

>>>>

Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. Moreover, in the examples, $\hat{\varphi}_\alpha(\zeta)$ turn out be an hypergeometric function of type ${}_pF_{p-1}$ where $p$ is the number of critical values. 
We expect that hypergeometric functions play a special role in resurgence theory as they may always appear when there are only finitely many singularities. In addition,  \textbf{Aaron-> what do you expect to be true in terms of the algebraic hypergeometric?}

### 2022-08-19 exp-resurgence.tex
Copy intro outline back into its old place

%%\let\Re\relax
%%\DeclareMathOperator{\Re}{Re}
\DeclareMathOperator{\Ai}{Ai}
\newcommand{\laplace}{\mathcal{L}}
\newcommand{\borel}{\mathcal{B}}
\newcommand{\deriv}[3]{\partial^{#1}_{#2 \text{ from } #3}}
\newcommand{\series}[1]{#1_\bullet}
%\input{command}
\title{Resurgence of the Airy function \\ and other exponential integrals}
\author{Veronica Fantini and Aaron Fenyes}

\begin{document}
\maketitle
\section{Introduction}
\subsection{Why does Borel resummation work?}
Borel resummation is a way of turning a formal power series
\[ \series{\varphi} = z^\sigma \left( \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \frac{\varphi_3}{z^4} + \ldots \right), \]
with $\sigma \in [0, 1)$, into a function which is asymptotic to $\series{\varphi}$ as $z \to \infty$. Different functions can be asymptotic to the same power series, and Borel resummation picks one of them, performing an implicit regularization~\textbf{[arXiv:1705.03071, or maybe arXiv:1412.6614]}. When a function matches the Borel sum of its asymptotic series, we'll say it's {\em Borel regular}. Several familiar kinds of regularity imply Borel regularity, and shed light on why it occurs.
%%Knowing that a function is Borel regular gives us extra information about it---enough to reconstruct it from its asymptotic series. What's the nature of this extra information?
%%Since different functions can be asymptotic to the same power series, Borel resummation must involve an {\em implicit regularization}, restricting its range to a class of functions which are uniquely determined by their formal power series.
\begin{itemize}
\item \textbf{Having a good asymptotic approximation}

>>>>

%%\let\Re\relax
%%\DeclareMathOperator{\Re}{Re}
\DeclareMathOperator{\Ai}{Ai}
\newcommand{\laplace}{\mathcal{L}}
\newcommand{\borel}{\mathcal{B}}
\newcommand{\deriv}[3]{\partial^{#1}_{#2 \text{ from } #3}}
\newcommand{\series}{\tilde}

\title{Resurgence of the Airy function \\ and other exponential integrals}
\author{Veronica Fantini and Aaron Fenyes}

\begin{document}
\maketitle
\section{Introduction}
\subsection{Motivation}
\subsubsection{Setting}
You can often find a formal power series
\[ \series{\Phi} = z^\sigma \left( \frac{c_0}{z} + \frac{c_1}{z^2} + \frac{c_2}{z^3} + \frac{c_3}{z^4} + \ldots \right), \]
with $\sigma \in [0, 1)$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, you might rewrite the integral
\color{DodgerBlue}
\[ \Phi(z) = \int_{\Lambda} \exp\left[-\tfrac{1}{12} z \left(4u^3 - 3u\right)\right]\,du \]
\color{black}
\[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(\tfrac{1}{3} u^3 - \tfrac{1}{4} u\right)\right]\,du \]
as
% see expansion.sage
\[ e^{z/12} \int_{-\infty}^\infty e^{-z\tau^2/2} \left[ 1 - \frac{2}{3} \tau + \frac{5}{6} \tau^2 - \frac{32}{27} \tau^3 + \frac{385}{216} \tau^4 - \frac{224}{81} \tau^5 + \frac{17017}{3888} \tau^6 - \ldots \right] d\tau \]
using the substitution $\tfrac{1}{2} \tau^2 = \tfrac{1}{3} u^3 - \tfrac{1}{4} u + \tfrac{1}{12}$. Na\"{i}vely integrating term by term, you get the series
\color{DodgerBlue}
\[ e^{z/12} z^{-1/2} \left[ (-1)!! + \frac{5}{6}\,1!!\,z^{-1} + \frac{385}{216}\,3!!\,z^{-2} + \ldots \right] \]
\[ e^{z/12} z^{1/2} \left[ \frac{(-1)!!}{z} + \frac{5}{6} \cdot \frac{1!!}{z^2} + \frac{385}{216} \cdot \frac{3!!}{z^3} + \frac{17017}{3888} \cdot \frac{5!!}{z^4} + \ldots \right] \]
\color{black}
\begin{equation}
e^{z/12} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{6} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{216} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{3888} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
\end{equation}
which has zero radius of convergence, but still makes sense as a formal power series. As another example, if you want to construct a holomorphic function $\Phi$ that satisfies the ordinary differential equation (ODE)
\begin{center}
\textbf{[shifted Bessel matching example above]},
\end{center}
you might start by trying to construct a formal power series solution instead. Observing that the leading term must be a multiple of $z^{-1/2}$ and then extending term by term, you again \textcolor{magenta}{[check]} get series~\eqref{series:bessel-ex}.
\item The series $\tilde{\phi}$ turns out to have a positive radius of convergence, so it defines a holomorphic function $\hat{\phi}$. By analytic continuation, we can expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
\subsubsection{Goals}
\item \textbf{A new dictionary for ODEs.} The Laplace transform is often usd to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain. We find, however, that it's much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain. This clarifies why we take the Borel sums at zeroes of $\lambda$ when we're trying to solve an ODE.
\item Some have been discussed many times, using different approaches and conventions. We'll try to give an idea of how all these different treatments fit together. $\bullet$ The Airy function. $\bullet$ The anharmonic oscillator (Bender--Wu, Schiappa).
\item \textcolor{magenta}{To understand, for example, the Ecalle formalism, you can start with these toy examples, which illustrate what's going on, but can also be studied in a more elementary way. [How do we work this into the introduction?]}
\color{DarkBlue}
\subsection{Why does Borel resummation work?}
Borel resummation is a way of turning a formal power series
\[ \series{\varphi} = z^\sigma \left( \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \frac{\varphi_3}{z^4} + \ldots \right), \]
with $\sigma \in [0, 1)$, into a function which is asymptotic to $\series{\varphi}$ as $z \to \infty$. Different functions can be asymptotic to the same power series, and Borel resummation picks one of them, performing an implicit regularization~\textbf{[arXiv:1705.03071, or maybe arXiv:1412.6614]}. When a function matches the Borel sum of its asymptotic series, we'll say it's {\em Borel regular}. Several familiar kinds of regularity imply Borel regularity, and shed light on why it occurs.
%%Knowing that a function is Borel regular gives us extra information about it---enough to reconstruct it from its asymptotic series. What's the nature of this extra information?
%%Since different functions can be asymptotic to the same power series, Borel resummation must involve an {\em implicit regularization}, restricting its range to a class of functions which are uniquely determined by their formal power series.
\item \textbf{Having a good asymptotic approximation}
